Model LF

### 2023-03-15 paper version Hamid test.Rmd
Commit

```{r}
plot(window(nl_g_01 - nl_g_bs1, start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

>>>>

```{r}
plot(window((abs(nl_g_01) - abs(nl_g_bs1)), start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window((abs(tax_g_01) - abs(tax_g_bs1)), start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
lines(window(nben_h_un_01 - nben_h_un_bs1), col= "green", lwd=2);
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window((abs(nben_h_un_01) - abs(nben_h_un_bs1)), start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```
